Proportional multi-state multiple-cohort life table model

### 2018-04-04 MSLT/MSLTdoc.Rmd
Working on inputs description and link to framwork

The data used here is for an example for Australia, however, this will be updated to link with the ITHIM-R modules (synthetic population, PIF calculations).

>>>>

###Inputs

Table 1 describes data needs for the PMSLT, the data used here is for an example for Australia, however, this will be updated to link with the ITHIM-R modules and additional work required to generate data inputs. Here, we expand on Table 1 with the aim of providing clear guidance for the PMSLT data needs.
